---
title: "Bachelor_clean"
author: "Julie Svinth Nielsen"
date: "24/11/2021"
output: html_document
---

```{r}
library(tidyverse)
library(readr)
library(dplyr)
library(lme4)
library(tidyr)
```

```{r}
df_big_final <- read_csv("df_big_final.csv")



```



```{r}


###### Bar plot

df_bar_overall <- df_big_final %>%
  ggplot(aes(week, oms, fill = intervention))+geom_bar( stat = "summary", position = "dodge")+ 
  xlab("Intervention week")+ ylab("Mean of sold products")

df_bar_overall
```

```{r}

###### VIOLIN

df_violin <- df_big_final %>%
  ggplot(aes(as.factor(week), oms, fill = intervention))+geom_violin()+ 
  xlab("Intervention week")+ ylab("Mean of sold products")

df_violin


# Week 1
df_violin_1 <- df_big_final %>%
  filter(week == 1) %>% 
  ggplot(aes(as.factor(week), oms, fill = intervention))+geom_violin()+
  facet_wrap(~ vare_grp)+
  xlab("Intervention week")+ ylab("Mean of sold products")

df_violin_1


# Week 2
df_violin_2 <- df_big_final %>%
  filter(week == 2) %>% 
  ggplot(aes(as.factor(week), oms, fill = intervention))+geom_violin()+
  facet_wrap(~ vare_grp)+
  xlab("Intervention week")+ ylab("Mean of sold products")

df_violin_2


# Week 3
df_violin_3 <- df_big_final %>%
  filter(week == 3) %>% 
  ggplot(aes(as.factor(week), oms, fill = intervention))+geom_violin()+
  facet_wrap(~ vare_grp)+
  xlab("Intervention week")+ ylab("Mean of sold products")

df_violin_3

```



```{r}

######### JITTER

# week 1 - only vegetables

df_jitter_veg_1 <- df_big_final %>%
  filter(week == 1 & vare_grp == "vegetables") %>% 
  ggplot(aes(as.factor(week), oms, color = intervention))+geom_jitter()+
  facet_wrap(~ intervention)+
  xlab("Intervention week")+ ylab("Mean of sold products")

df_jitter_veg_1

# week 2 - only vegetables

df_jitter_veg_2 <- df_big_final %>%
  filter(week == 2 & vare_grp == "vegetables") %>% 
  ggplot(aes(as.factor(week), oms, color = intervention))+geom_jitter()+
  facet_wrap(~ intervention)+
  xlab("Intervention week")+ ylab("Sold products")

df_jitter_veg_2

# week 1- jitter


df_jitter_1 <- df_big_final %>%
  filter(week == 1) %>% 
  ggplot(aes(as.factor(week), oms, color = vare_grp))+geom_jitter()+
  facet_wrap(~ intervention)+
  xlab("Intervention week")+ ylab("Sold products")

df_jitter_1


# week 2- jitter

df_jitter_2 <- df_big_final %>%
  filter(week == 2) %>% 
  ggplot(aes(as.factor(week), oms, color = vare_grp))+geom_jitter()+
  facet_wrap(~ intervention)+
  xlab("Intervention week")+ ylab("Sold products")

df_jitter_2

# week 3 - jitter

df_jitter_3 <- df_big_final %>%
  filter(week == 3) %>% 
  ggplot(aes(as.factor(week), oms, color = vare_grp))+geom_jitter()+
  facet_wrap(~ intervention)+
  xlab("Intervention week")+ ylab("Sold products")

df_jitter_3




######### Density


dens_big <- df_big_final %>%
  filter(week == 1 & vare_grp == "vegetables") %>% 
  ggplot(aes(oms, color = intervention))+geom_density()
  
dens_big
```


```{r}

m0 <- lm(oms  ~ intervention, data = df_big_final, REML = FALSE)
m1 <- lmer(oms  ~ intervention + (1|vare_grp), data = df_big_final, REML = FALSE)

m2 <- lmer(oms  ~ intervention + (1|vare_grp)+ (1|week), data = df_big_final, REML = FALSE)



df_big_final$week <- as.numeric(df_big_final$week)


# Exploring intevention 1 and 2
df_week_1_2 <- filter(df_big_final, week <= 2)

m_1_2 <- lmer(oms ~ intervention + (1|vare_grp), data = df_week_1_2, REML = F)
summary(m_1_2)

# Exploring intervention 1 and 3
df_week_1_3 <- filter(df_big_final, week != 2)
m_1_3 <- lmer(oms ~ intervention + (1|vare_grp), data = df_week_1_3, REML = F)
summary(m_1_3)

pairwise.t.test(df_week_1_3$oms, df_week_1_3$intervention, p.adjust.method="bonferroni")

# Exploring intervention 2 and 3
df_week_2_3 <- filter(df_big_final, week >= 2)
m_2_3 <- lmer(oms ~ intervention + (1|vare_grp), data = df_week_2_3, REML = F)
summary(m_2_3)


pairwise.t.test(df_week_1_2$oms, df_week_1_2$intervention, p.adj = "bonf")
pairwise.t.test(df_week_1_3$oms, df_week_1_3$intervention, p.adj = "bonf")
pairwise.t.test(df_week_2_3$oms, df_week_2_3$intervention, p.adj = "bonf")


summary(m0)
summary(m1)
summary(m2)

plot(m1)

df_big_final$intervention <- as.factor(df_big_final$intervention)

m_full <- lmer(oms ~ )

```

####### Help from Tylén 
```{r}

# Create data frames for each week
df_week_1 <- filter(df_big_final, week != 2 & week !=3)

df_week_2 <- filter(df_big_final, week != 1 & week !=3)

df_week_3 <- filter(df_big_final, week != 1 & week !=2)


# Week 1 - create difference column and remove reference rows
df_week1_ref <-filter(df_week_1, intervention != "label")
df_week1_ref <- na.omit(df_week1_ref)

df_week1_ref <- df_week1_ref %>% 
  select("vare", "oms")

df_week1_lab <-filter(df_week_1, intervention != "reference")
df_week1_lab <- na.omit(df_week1_lab)

df_week_1_new <- left_join(df_week1_lab,df_week1_ref, by = "vare")



df_week_1_new$diff <- df_week_1_new$oms.x - df_week_1_new$oms.y

write.csv(x=df_week_1_new, file="df_w_1.csv")

# Week 2 create difference column

df_week2_ref <-filter(df_week_2, intervention != "nudge")

df_week2_nud <-filter(df_week_2, intervention != "reference")

df_week2_ref <- df_week2_ref %>% 
  select("vare", "oms")

df_week_2_new <- left_join(df_week2_nud,df_week2_ref, by = "vare")

df_week_2_new$diff <- df_week_2_new$oms.x - df_week_2_new$oms.y

write.csv(x=df_week_2_new, file="df_w_2.csv")

# Week 3 - create difference column


df_week3_ref <-filter(df_week_3, intervention != "inspiration")

df_week3_insp <-filter(df_week_3, intervention != "reference")

df_week3_ref <- df_week3_ref %>% 
  select("vare", "oms")

df_week_3_new <- left_join(df_week3_insp,df_week3_ref, by = "vare")

df_week_3_new$diff <- df_week_3_new$oms.x - df_week_3_new$oms.y

write.csv(x=df_week_3_new, file="df_w_3.csv")


```

Model making
```{r}

# Load in data
df_w_1 <- read_csv("df_w_1.csv")
df_w_2 <- read_csv("df_w_2.csv")
df_w_3 <- read_csv("df_w_3.csv")


# Hypothesis 1
t.test(df_w_1$diff, mu = 0, alternative = "greater")


# Hypothesis 2
t.test(df_w_2$diff, mu = 0, alternative = "greater")

# Hypothesis 3

t.test(df_w_3$diff, mu = 0, alternative = "greater")
```
Access to the values returned by t.test() function
The result of t.test() function is a list containing the following components:


statistic: the value of the t test statistics
parameter: the degrees of freedom for the t test statistics
p.value: the p-value for the test
conf.int: a confidence interval for the mean appropriate to the specified alternative hypothesis.
estimate: the means of the two groups being compared (in the case of independent t test) or difference in means (in the case of paired t test).

Visualization
```{r}

df_overall <- rbind(df_w_1, df_w_2, df_w_3)

df_overall$intervention <- as.factor(df_overall$intervention)

df_overall %>%
  group_by(intervention) %>%
  summarise(mean_diff = mean(diff, na.rm = T), se = sd(diff, na.rm = T)/(sqrt(length(diff)))) %>% 
  ggplot(aes(intervention, mean_diff, color = intervention)) +
  geom_point() +
  geom_errorbar(aes(ymin=mean_diff-se, ymax=mean_diff+se), width=.2,
                position=position_dodge(.9))


```

Hypothesis 4
```{r}

# Relevel intervention - label as baseline
df_overall$intervention <- relevel(df_overall$intervention, ref = "label")

# Does nudging have a significant greater effect than labeling?
m1 <- lmer(diff ~ intervention + (1|vare_grp), data = df_overall)

summary(m)
```


```{r}
# Does inspiration have a greater effect than the two other interventions

# Relevel intervention - inspiration as baseline
df_overall$intervention <- relevel(df_overall$intervention, ref = "inspiration")

m2 <- lmer(diff ~ intervention + (1|vare_grp), data = df_overall)

summary(m2)
```

